Large squeezing in Bose-Einstein condensates with large numbers of atoms

### 2013-07-11 large_number_squeezing_with_atoms.tex
Fix figure axis labels and font sizes

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=7cm]{figures/dimensional_effects_on_squeezing_1.eps}
    \label{figDimensionalSqueezingEffects:sub1}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=7cm]{figures/dimensional_effects_on_squeezing_2.eps}
    \label{figDimensionalSqueezingEffects:sub2}
  \end{subfigure}
\caption{Effects of dimension on squeezing in two different nonlinear regimes, assuming that the chemical potential is constant for all simulations. If two nonlinearities are non-zero, the deleterious effects of higher dimensions on squeezing are exacerbated. Thick red line, analytic two-mode solution; solid blue line, 1D; dashed line, 2D; dash-dotted line, 3D. (a) Parameters: $n_a = n_b =2 \times 10^5$, $\chi_{aa}=\chi_{bb}=0.03\,\text{s}^{-1}$, $\chi_{ab}=0$, $\tau_{\mathrm{hold}}=3\times 10^{-4}$s, $\phi=6.2$. (b) $n_a = n_b =2 \times 10^5$, $\chi_{aa}=0.03\,\text{s}^{-1}$, $\chi_{bb}=\chi_{ab}=0$, $\tau_{\mathrm{hold}}=3\times 10^{-4}$s, $\phi=3.1$.}
  \label{figDimensionalSqueezingEffects}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=6cm]{figures/dimensional_effects_on_squeezing_1.eps}
    \label{figDimensionalSqueezingEffects:sub1}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=6cm]{figures/dimensional_effects_on_squeezing_2.eps}
    \label{figDimensionalSqueezingEffects:sub2}
  \end{subfigure}
\caption{Effects of dimension on squeezing in two different nonlinear regimes, assuming that the chemical potential is constant for all simulations. If two nonlinearities are non-zero, the deleterious effects of higher dimensions on squeezing are exacerbated. Thick red line, analytic two-mode solution; solid blue line, 1D; dashed line, 2D; dash-dotted line, 3D. (a) Parameters: $n_a = n_b =2 \times 10^5$, $\chi_{aa}=\chi_{bb}=0.03\,\text{s}^{-1}$, $\chi_{ab}=0$, $\tau_{\mathrm{hold}}=3\times 10^{-4}$s, $\phi=6.2$. (b) $n_a = n_b =2 \times 10^5$, $\chi_{aa}=0.03\,\text{s}^{-1}$, $\chi_{bb}=\chi_{ab}=0$, $\tau_{\mathrm{hold}}=3\times 10^{-4}$s, $\phi=3.1$.}
  \label{figDimensionalSqueezingEffects}
\end{figure}
